---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# whotilities

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/caldwellst/whotilities.svg?branch=master)](https://travis-ci.com/caldwellst/whotilities)
<!-- badges: end -->

The goal of whotilities is to provide a package where useful and commonly needed functionality is
made available to R users working at the World Health Organization. 
At the moment, this is a set of functions to work with country
codes and names, allowing easy conversion between names and codes and access to regions and
WHO member status.

## Functions

Some functions are built to help you turn names or country codes into ISO3 codes:

* `names_to_code()` is the workhorse function that helps match country names and returns standardized country codes.
* `codes_to_iso3()` converts other country codes into ISO3 format.
* `valid_codes()` lets you quickly check which country codes in a vector are recognized by the whotilities package.

Other functions encourage a tidy R workflow where ISO3 codes are used as the unique identifier for each country:

* `iso3_to_regions()` takes in a vector of ISO3 codes and returns specified region values.
* `iso3_to_codes()` takes in a vector of ISO3 codes and returns specified country codes.
* `iso3_to_names()` takes in a vector of ISO3 codes and returns specified country names.
* `is_who_member()` takes in a vector of ISO3 codes and checks if they are a WHO member state or not.

All of these functions are built on top of the `countries` data frame also exported
with the package and developed off of public datasets provided by the World Health
Organization and United Nations. Details available through `?countries`.

## Installation

You can install whotilities from Github with:

``` r
devtools::install_github("caldwellst/whotilities")
```

## Usage

If we have an unclean data frame with country names, we can use `names_to_codes()`
to match these to ISO3 codes. The function matches the names vector across all possible
names found in the `countries` data frame. ISO3 codes for exact matches are always returned,
but the user has specific options for non-exact matches. They can be fuzzy matched (the default),
always made NA, or require user input to confirm fuzzy matching results. Fuzzy matches
always return a message to the user on the confirmed match. More details available through
`?names_to_codes`.

```{r names_to_code}
library(whotilities)

names_to_code(c("Venezuela", "Arentina", "afghanist"))
```

Since these functions are vectorized, we can easily use them in a normal workflow, especially
if we're using the `tidyverse`. Below, we can clean up our tidy names and get
the correct UN region and income group for our countries, as well as its name
in Chinese:
```{r last_example}
library(dplyr, quietly = TRUE)
df <- data.frame(c_names = c("Venezuela", "Arentina", "afghanist"))

df %>%
  mutate(iso3 = names_to_code(c_names),
         un_region = iso3_to_regions(iso3, region = "un_region"),
         wb_ig = iso3_to_regions(iso3, region = "wb_ig"),
         name_zh = iso3_to_names(iso3, org = "un", language = "zh"))
```
