---
title: "Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

If we have an unclean data frame with country names, we can use `names_to_codes()`
to match these to ISO3 codes. The function matches the names vector across all possible
names found in the `countries` data frame. ISO3 codes for exact matches are always returned,
but the user has specific options for non-exact matches. They can be fuzzy matched (the default),
always made NA, or require user input to confirm fuzzy matching results. Fuzzy matches
always return a message to the user on the confirmed match. More details available through
`?names_to_codes`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r names_to_code}
library(whoville)

names_to_code(c("Venezuela", "Arentina", "afghanist"))
```

Since these functions are vectorized, we can easily use them in a normal workflow, especially
if we're using the `tidyverse`. Below, we can clean up our tidy names and get
the correct UN region and income group for our countries, as well as its name
in Chinese:

```{r last_example, message=F}
library(dplyr)
df <- data.frame(c_names = c("Venezuela", "Arentina", "afghanist"))

df %>%
  mutate(iso3 = names_to_code(c_names),
         un_region = iso3_to_regions(iso3, region = "un_region"),
         wb_ig = iso3_to_regions(iso3, region = "wb_ig"),
         name_zh = iso3_to_names(iso3, org = "un", language = "zh"))
```

